---
title: "Eating Out"
author: "Leilani Guerrero"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "Summer 2022"    
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The data comes from the 1998 General Social Survey answer this question

$H_0$ There is no difference among the various races with frequency of eating out  
$H_A$ There is a statistical difference between at least two races with the frequency of eating out  


```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
GSS <-read.dta(file="GSS1998.dta")
GSS <- droplevels(GSS)
mydata <- select(GSS,race,age,eatout)
mydata <- na.omit(mydata)
```

## Methods

The response variable is categorical: dine out last week? yes or no
explanatory variable is race, it too is a categorical variable.
so we use cat~cat
Inference: chi-squared and fisher exact tests

# Descriptive summaries

## Graphical summary

```{r}
barchartGC(~race + eatout,data=mydata)
barchartGC(~race + eatout,data=mydata, type="percent")

```

According to the graph, the race "white" has the highest percentage and frequency of going out to eat with a frequency of over 800 and a percentage of over 80%. However, race "other" has the second highest percentage of going out to dinner with 70% and the lowest frequency of going out to dinner of below. Race "black" has the lowest percentage of going out to dinner with under 70% and the second highest frequency of going out to dinner with 100.


 ## Numerical summary
```{r}
table1 <- xtabs(~race + eatout, data=mydata)
rowPerc(table1)
colPerc(table1)
```

This table shows that out of 100 race "white", 83.11 responded to yes to eating out and 16.89 said no. Out of 100 race "black", 69.04 responded to yes to eating out and 30.96 said no. Out of 100 race "other", 72.12 responded to yes to eating out and 27.88 said no. Also, out of 100 races; 81.75 responded to yes are white, 11.76 are black and 6.49 are other. And out of 100 races; 68.09 responded to no are white, 21.63 are black and 10.28 are other. Which means out of all the races the race white are more likely to go out to eat. 


# Results

## Inferential results

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```


reject null hyp


