---
title: "Eating Out"
author: "Leilani Guerrero"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "Summer 2022"    
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The data comes from the 1998 General Social Survey answer this question

$H_0$ There is no difference among the various races with frequency of eating out  
$H_A$ There is a statistical difference between at least two races with the frequency of eating out  


```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
GSS <-read.dta(file="GSS1998.dta")
GSS <- droplevels(GSS)
mydata <- select(GSS,race,age,eatout)
mydata <- na.omit(mydata)
```

## Methods

The response variable is categorical: dine out last week? yes or no
explanatory variable is race, it too is a categorical variable.
so we use cat~cat
Inference: chi-squared and fisher exact tests

# Descriptive summaries

## Graphical summary

```{r}
barchartGC(~race + eatout,data=mydata)
barchartGC(~race + eatout,data=mydata, type="percent")

```

According to the graph, the race "white" has the highest percentage and frequency of going out to eat with a frequency of over 800 and a percentage of over 80%. However, race "other" has the second highest percentage of going out to dinner with 70% and the lowest frequency of going out to dinner of below. Race "black" has the lowest percentage of going out to dinner with under 70% and the second highest frequency of going out to dinner with 100.


 ## Numerical summary
```{r}
table1 <- xtabs(~race + eatout, data=mydata)
rowPerc(table1)
colPerc(table1)
```
this table shows that white people eatout more then the other racses 


# Results

## Inferential results

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```


reject null hyp


